paper1_results_figs_slimmed_50_rr

### 2016-11-11 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
tweaking paper1 figs

## Figures for paper 1 : version 9 : looking at producing Tiffs for submission

## using rr_restoration instead of selection coefficient

### automagically generated by R from paper1_results_figs_slimmed_50_rr.Rmd

## Notable results

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) adaptive mixture, switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure and dominance have the greatest on time-to-resistance as shown in PRCC analyses.
1. Effectiveness of the insecticides is the one input that can change the average relative positioning of the strategies a) sequential and b) adaptive mixture. Below an effectiveness of ~0.55 to 0.6 sequential takes longer to reach the resistance threshold, and above this the adaptive mixture takes longer. 
1. Exposure and effectiveness come out as the most important effect on the difference between the sequential and adpative mixture strategies.
1. Exposure and effectiveness can be used to predict most of whether resistance will arise slower under the sequential or adaptive mixture strategy, either by a simple plot or using classification trees.
1. The implication of additional operational costs of adaptive mixtures can be investigated. If a requirement of a 20% improvement in resistance is imposed then more runs favour sequential than mixture.

@@

plotlist[[2]] <- ggplot(data.frame(x=c(0,100),y=c(80,0)), aes(x=x, y=y)) + 
       theme_bw() + 
       ylim(0,100) +   
       ylab("Insecticide concentration") +
       xlab("Time since treatment") +         
       geom_line(size=2, colour=rgb(0.5,0,0.5)) +
       geom_vline(xintercept = c(20,40,60), linetype=2) +
       geom_text(data=df_labs,aes(x=x, y=y, label=lab, colour=factor(col)),size=4) +
       scale_colour_manual(values = c("0" = "red","0.5" = "orange","1" = "green"), guide=FALSE) +  
       geom_label(data=df_boxes,aes(x=x, y=y, label=lab)) +
       theme(axis.text = element_blank(),
             axis.ticks = element_blank(),
             panel.grid = element_blank())
       #draw_plot_label('B)') +

@@

  library(png)
  f1png <- readPNG(system.file("documents","pap1_curtis1.png", package="resistance"))
  plot( 0, 0, type="n", axes=F, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="")
  rasterImage(f1png, xleft=0, ybottom=0, xright=1, ytop=1, interpolate = FALSE)
  mtext('A)',side=3, adj=0, line=1)

>>>>

## Figures for paper 1 : version 9 : produces Tiffs for submission (fails to produce pdf due to tiff options set in first chunk)
## using rr_restoration instead of selection coefficient

@@

plotlist[[2]] <- ggplot(data.frame(x=c(0,100),y=c(80,0)), aes(x=x, y=y)) + 
       theme_bw() + 
       ylim(0,100) +
       coord_cartesian(expand = FALSE) + #so that axes fit data exactly
       ylab("Insecticide concentration") +
       xlab("Time since treatment") +         
       geom_line(size=2, colour=rgb(0.5,0,0.5)) +
       geom_vline(xintercept = c(20,40,60), linetype=2) +
       geom_text(data=df_labs,aes(x=x, y=y, label=lab, colour=factor(col)),size=4) +
       scale_colour_manual(values = c("0" = "red","0.5" = "orange","1" = "green"), guide=FALSE) +  
       geom_label(data=df_boxes,aes(x=x, y=y, label=lab)) +
       theme(axis.text = element_blank(),
             axis.ticks = element_blank(),
             panel.grid = element_blank())
       #draw_plot_label('B)') +

@@

  library(png)
  f1png <- readPNG(system.file("documents","pap1_curtis1.png", package="resistance"))
  #both the ld and the rfreq plots (ld on its own means little with the way axes are labelled)
  #f1png <- readPNG(system.file("documents","pap1_curtis1_both.png", package="resistance"))
  plot( 0, 0, type="n", axes=F, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="")
  rasterImage(f1png, xleft=0, ybottom=0, xright=1, ytop=1, interpolate = FALSE)
  mtext('A)',side=3, adj=0, line=1)
